\documentclass[12pt]{article} % font size here: some require 11 or 12 point
\usepackage{setspace}
\usepackage{fancyvrb}
\usepackage{epsfig}
\usepackage{fullpage}
\usepackage[small,compact]{titlesec}
\usepackage{times} 
\usepackage{enumitem}
\usepackage{wrapfig}
\setlength{\topmargin}{+0.0in}   %%%%%%%%% this is hacked (from +.0.1in) so that it looks right when converted.
\setlength{\oddsidemargin}{-0.0in}
\setlength{\evensidemargin}{-0.0in}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.5in}
\usepackage[margin=1.0in,headheight=0pt,footskip=20pt,headsep=0.2in]{geometry}
\usepackage{natbib}
% ----------------------------------------------------
\usepackage{setspace}
\onehalfspacing % may need to switch to single spacing

\usepackage{natbib}
\usepackage{color}
\bibliographystyle{apj}
\newcommand{\apj}{ApJ}
\newcommand{\apss}{Astrophysics and Space Science}
\newcommand{\aj}{AJ}
\newcommand{\apjl}{ApJL}
\newcommand{\mnras}{MNRAS}
\newcommand{\apjs}{ApJS}
\newcommand{\pasp}{PASP}
\newcommand{\araa}{ARA\&A}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\pasj}{PASJ}
\newcommand{\prd}{Phys. Rev. D}
\newcommand{\nat}{Nature}
\newcommand{\nar}{New Astronomy Review}
\newcommand{\ao}{Applied Optics}
\newcommand{\physrep}{Physics Reports}
\newcommand{\etal}{et al}
\def\subsun{\mbox{$_{\odot}$}}
\def\lesssim{\mathrel{\hbox{\rlap{\hbox{%
 \lower4pt\hbox{$\sim$}}}\hbox{$<$}}}}
\def\gtrsim{\mathrel{\hbox{\rlap{\hbox{%
 \lower4pt\hbox{$\sim$}}}\hbox{$>$}}}}
\RequirePackage{natbib}
%\usepackage{setspace}
\setlength{\bibsep}{0.0pt}
\newenvironment{itemize*}%
{\begin{itemize}%
  \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
{\end{itemize}}

\newenvironment{enumerate*}%
{\begin{enumerate}%
  \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
{\end{enumerate}}

\usepackage{fancyhdr}
\pagestyle{fancy}


\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Andrew Emerick}
\rhead{}

%\usepackage[pagestyles]{titlesec}
%\newpagestyle{mystyle}{\sethead{}{}{Name -- Number}\setfoot{}{\thepage}{}}
%\pagestyle{mystyle}

\title{\vspace{-5ex} Performance and Scaling Tests
       \vspace{-2ex}}

\begin{document} \thispagestyle{empty}

% Star-by-Star Stellar Feedback and Chemical Evolution in Dwarf Galaxies

\maketitle

\textsc{Enzo} has been used extensively a range of large-scale computing resources including XXXX, in addition to both \textsc{Stampede} and \textsc{Stampede-2}, the proposed resource. Generally, \textsc{Enzo} has been shown to achieve very good weak scaling in unigrid cosmological simulations on up to 4096 cores, and speed-ups in strong scaling tests of a 512$^3$ AMR simulation with 6 levels of refinement on up to 4096 cores. We present here the performance and scaling properties of \textsc{Enzo} in the particular context of typical computational loads of our proposed cosmological simulations. 

In this situation, we are primarily concerned with the strong scaling properties of \textsc{Enzo} given our proposed problem size, AMR hierarchy depth, and included physics in order to find the optimum core / node count and node type (SKX or KNL) for our desired problem. We first outline the numerical methods employed in \textsc{Enzo} to achieve high-performance and good scaling on HPC systems.

\section{Computational Methods and Problem}

Our AMR cosmological simulations are initialized in a (1~Mpc co-moving)$^3$ box with a 256$^3$ root-grid of cells and dark matter particles, with a maximum of 12 levels of refinement to a resolution of 1~pc co-moving. 

\subsection{Hydrodynamics and Gravity}
\textbf{Below is copy pasted... needs to be heavily shortened... was probably too detailed last time...}

\texttt{Enzo} is equipped with multiple, distinct hydrodynamics solvers. For this work we employ a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995}. This is an explicit, higher-order accurate version of Godunov's method for ideal gas hydrodynamics that uses spatially third-order accurate piecewise parabolic monotonic interpolation. Shock capturing is handled with a nonlinear Riemann solver. This base method is extended to multiple dimensions using directional splitting, resulting in a final algorithm that is second-order accurate in space and time; we explicitly conserve mass, linear momentum, and energy \citep{Hawley1984, NormanWinkler1986}. We use a dual energy formalism to track the total energy and thermal energy separately, preventing substantial numerical errors that arise when the thermal energy is very small compared to the total energy (i.e. when the kinetic energy is large). We default to using the two-shock approximate Riemann solver \citep{Toro1997}, with progressive fallback to more diffusive approximate Riemann solvers when higher order methods produce negative densities or energies \citep{LemasterStone2009}. In this situation, we fall back to either the Harten-Lax-van Leer (HLL) \citep{Toro1997} method with contact discontinuities -- a three-wave, four-state solver -- or the basic HLL -- a two-state, three-wave solver. The hydrodynamics time step is set by the Courant-Friedrichs-Levy (CFL) condition for stability, scaling linearly with cell size ($\Delta x$) and inversely proportional to the sum of the bulk velocity and sound speed in each cell in a given direction. The multidimensional CFL limited time step is the harmonic average of the limiting CFL time step in each dimension. 

Gas self-gravity and the gravitational forces of the massive star particles are computed together to compute the gravitational acceleration on each cell and particle. On the root grid, we use a cloud-in-cell (CIC) method \citep{HockneyEastwood1988} to map particles to a time-centered density field, including the effects of particles across sub-grids and neighboring domains; a similar time-centered density field is computed for the baryons in each grid cell. The gravitational potential is solved for using a fast Fourier transform (FFT) in isolated boundary conditions \citep{James1977}; accelerations are computed with a two-point centered difference scheme using the transformed real-space potential. For accuracy on sub-grids, we employ the seven-point, second-order finite difference approximation to Poisson's equation, solving the given Dirichlet boundary conditions with multigrid relaxation. Unwanted oscillations and errors across grids are reduced using expanded buffer zones around each grid, coupled with an iterative relaxation process between sibling grids. Particle accelerations are computed from the grid potential using linear CIC mapping. \texttt{Enzo} employs the particle-mesh N-body method from \cite{HockneyEastwood1988} to evolve the colissionless star particles with an effective force resolution of approximately 2$\Delta x$.

\subsection{Grid Hierarchy and Parallelization Strategy}

\texttt{Enzo} AMR simulations begin with a defined rectilinear root grid encompassing the computational domain. Additional levels of refinement take the form of child sub-grids nested within the root grid, generating a nested tree comprised of grid parents, children, and siblings; for our purposes, additional sub-grids increase resolution by a factor of two. Each grid is comprised of active zones and ghost zones that store boundary information from sibling grids. Each level in this tree is evolved on independent time steps, reducing unneeded computation on lower levels of refinement.

Using grid objects as fundamental units that exist entirely on a single processor, \texttt{Enzo} has been parallelized with the message passing interface (MPI). Grids are therefore distributed among processors in such a way to attempt to balance the computational load across processors. This is simple for the root grid, which is evenly divided in tiles to all processors, but is more complicated for higher refinement levels, which usually are not uniformly distributed in the simulation volume. Higher levels of refinement are initially placed on the processors that host their parent grids, but are subsequently distributed among other processors to reduce computational load. Load is estimated as the number of active zones on each grid. We use a simple load-balancing option to progressively move grids from processors with high computational loads to processors with the lowest computational loads until the load ratio of the most-to-least loaded processors is less than 1.05. To improve performance further, \texttt{Enzo} dynamically adjusts the size of each sub-grid on a given level depending on the number of zones on the given level and the load balance across processors on that level. This reduces communication time across processors on each level while also improving the effectiveness of load-balancing. 

Each processor contains a copy of the entire grid hierarchy meta data, allowing for easy non-blocking communication across processors; the additional memory overhead of storing this data on each processor is negligible. In addition, all star particle information is stored on each processor (again, with negligible memory overhead), removing the need for communication when injecting feedback from stars close to grid boundaries.

\subsection{Radiative Transfer Methods}

\cite{WiseAbel2011} implemented radiative transfer capabilities in \texttt{Enzo}, performing rigorous tests of its capabilities, and has been used in a variety of applications \citep[e.g.][]{Wise2012a,WiseAbel2012,Wise2014, Smith2015, OShea2015, Koh2016, Regan2016a, Regan2016b}. The equations of radiative transfer are solved directly on the computational domain following directly traced rays from individual point sources. This is an inherently computationally expensive process. To improve efficiency \texttt{Enzo} employs an adaptive ray tracing method \citep{AbelWandelt2002} where rays are mapped from a point source to HEALPix pixels surrounding the source. The resulting rays are advanced through the grid, progressively refining rays by splitting them into child rays once the ratio of the cell face area to ray solid angle drops sufficiently. In a given time step, rays propagate a distance $c\times dt$, or until they either leave the computational domain or their flux drops by 99.99\% or more in a single cell. If the rays still exist at the end of the ray tracing step, their evolution is halted and stored for the next time step. The resulting ionization and heating rates due to the radiation field are computed assuming the photo-ionization and absorption rate are equal, ensuring photon conservation \citep{Abel1999, Mellema2006}. These are passed to the \texttt{Grackle} chemistry solver to update the correct ionization, chemical, and energy states in each cell.

\section{Performance and Scaling Results}

Profiling the exact scaling and performance results of a cosmological AMR simulation is challenging, as the total number of computational grids can vary significantly over a run. In general, however, computational expense will increase as a simulation progresses as the number of cells grow to follow dense, star forming gas, and the number of star particles grows. 

\def\bibfont{\footnotesize}
\bibliographystyle{apj}
\bibliography{msbib}%\thispagestyle{empty}


\end{document}
